### 2015-02-27 icfp15-servo/rust.tex
Add some XXX comments.
Fix up comment about data parallelism

Data parallelism is a bit more tricky today because there is no way to \eg{} partition a vector in safe code
for a data parallel operation and then stitch it back together afterwards without performing a copy of the data.

>>>>

There is partial support for data parallelism, in the form of partitioning a vector statically in advance
and transferring ownership of each of those partitions into newly spawned threads.
But, it is not possible in safe Rust code to write work-stealing algorithms~\cite{blumeofe:multiprogrammed-work-stealing}
that dynamically parition and adjust work across threads.
